Dish: Distribution-oblivious Shell Scripting

### 2020-01-03 osdi/draft.tex
Dump notes

>>>>

\section{Introduction}
\label{intro}

Distributed systems offer significant benefits over their centralized counterparts---for example, they can speed up expensive computations or can process data that would not fit into any single machine.
Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
Whereas anyone can quickly stitch together a Bash script to compute on a single computer, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{taurus:14, dios:13, andromeda:15, pywren:17, futuredata:18, nefele:18}.
% 
To understand this sharp contrast, consider a Bash pipeline calculating term frequencies over a set of inputs:

Contributions:

* 
Extends beyond linear pipelines to full programs 
that comply with the POSIX shell specification; while \sys does not optimize
everything---it certainly cannot---, it does

* Planner activations, the ability to call

* A standard library of semantics-aware wrappers for

* Augment data flows to allow performance optimizations and fault-tolerance

\section{Background}
\label{bg}

To understand the limitations of pipelines and the opportunities for
parallelization, consider the following pipeline

\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
find . -name '*.sh' | xargs cat | wc -l > out.t
\end{lstlisting}

Unfortunately, this pipeline meshes the results from `cat` leading to a single
count from all files. What the developer actually intended was the following:

\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
$(
for f in $(find . -name '*.sh'); do
 cat ${f} | wc -l
done
) > out.t
\end{lstlisting}

This remains trivial to parallelize, as none of the loop-internal steps depends
on the input, so loop iterations can run in parallel.

Similar for
  * enclaves 
  * sieve
  * mapping max temperatures to years, etc.

Different from prior systems, \sys's goal is to ensure correctness first and
then improve performance.

\section{Evaluation}

\subsection{POSIX test-suite}

\subsection{Pipelines and scripts}

\subsection{Other pipelines}

Rewrite pipelines expressed in other languages / scripts
